One page description

### 2016-09-27 publications/Journal/7-related-work.tex
Update Related Work with reviewer comments.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

Previous \textsf{DEVS} simulation tools have already implemented multiple synchronization protocols, though none have done it in a strictly modular way that allows straightforward protocol switching for a single given model.
For example, \textit{adevs} only supports conservative synchronization, and \textit{vle} only supports experiment-level parallelism (\textit{i.e.}, run multiple experiments concurrently).
Closest to our support for multiple synchronization protocols is \textit{CD++}~\cite{CD++}.
For \textit{CD++}, both a conservative (\textit{CCD++}~\cite{CCD++}) and optimistic (\textit{PCD++})~\cite{PCD++}) variant exist.
Despite the implementation of both protocols, they are different projects entirely.
Some features might therefore be implemented in \textit{CCD++} and not in \textit{PCD++}, or vice versa.
And while this might not yet be that significant a problem to this day, this problem will only get worse when each project follows its own course.
\textit{Dxex}, on the other hand, is a single project, where the choice of synchronization protocol is a simple configuration.
\textit{CD++}, however, implements both conservative and optimistic synchronization for distributed simulation, whereas we limit ourselves to parallel simulation.
By limiting our approach to parallel simulation, we are able to achieve higher speedups through the use of shared memory communication.

@@

Model allocation and its impact on parallel performance has previously also been studied in the \textsf{PDES} community~\cite{PDESpartitioning}.
Referenced as partitioning of the simulation model, most studies distinguish between communication overhead and computational distribution (load balancing) as the two dimensions to partition over.
Partitioning a simulation model is identified as an issue to achieve scalability~\cite{Scalability}. 
Some research in the context of \textsf{Parallel DEVS} has been done, where they turn their attention to load balancing and communication overhead~\cite{PDEVSpartitioning}.
Our contribution studies the effect of partitioning with emphasis on the effect of communication between processes and in the presence of a flattened hierarchy. 
We focus on static partitioning since this is a limiting factor for our conservative synchronization implementation which does not support model relocation.
Model relocation, as implemented by \textit{PythonPDEVS}~\cite{PythonPDEVS2}, might be an interesting addition to only model allocation at the start of simulation.

>>>>

Previous \textsf{DEVS} simulation tools have already implemented multiple synchronization protocols, though none have done it in a strictly modular way that allows straightforward protocol switching for a single given model.
For example, \textit{adevs} only supports conservative synchronization, and \textit{vle} only supports experiment-level parallelism (\textit{i.e.}, run multiple experiments concurrently).
Closest to our support for multiple synchronization protocols is \textit{CD++}~\cite{CD++}.
For \textit{CD++}, both a conservative (\textit{CCD++}~\cite{CCD++}) and optimistic (\textit{PCD++})~\cite{PCD++}) variant exist.
Despite the implementation of both protocols, they are different projects entirely.
Some features might therefore be implemented in \textit{CCD++} and not in \textit{PCD++}, or vice versa.
And while this might not yet be that significant a problem to this day, this problem will only get worse when each project follows its own course.
\textit{Dxex}, on the other hand, is a single project, where the choice of synchronization protocol is a simple configuration.
\textit{CD++}, however, implements both conservative and optimistic synchronization for distributed simulation, whereas we limit ourselves to parallel simulation. 
A new architecture for sequential PDEVS simulation has been introduced in \cite{SeqPDEVSArch} with promising performance results. This algorithm achieves a speedup by using the inherent parallelism in PDEVS without the need for synchronization.
By limiting our approach to a pure parallel simulation, we are able to achieve higher speedups through the use of shared memory communication.

@@

Model allocation and its impact on parallel performance has previously also been studied in the \textsf{PDES} community~\cite{PDESpartitioning}.
Referenced as partitioning of the simulation model, most studies distinguish between communication overhead and computational distribution (load balancing) as the two dimensions to partition over.
Partitioning a simulation model is identified as an issue to achieve scalability~\cite{Scalability}. 
Some research in the context of \textsf{Parallel DEVS} has been done, where they turn their attention to load balancing and communication overhead~\cite{PDEVSpartitioning, NonFragmenting}.
Our contribution studies the effect of partitioning with emphasis on the effect of communication between processes and in the presence of a flattened hierarchy. 
We focus on static partitioning since this is a limiting factor for our conservative synchronization implementation which does not support model relocation.
Model relocation, as implemented by \textit{PythonPDEVS}~\cite{PythonPDEVS2}, might be an interesting addition to only model allocation at the start of simulation.
